### 2025-05-09 paper/abs_en.tex
feat: polish19

In the process of modern agriculture's transformation towards intelligence, precision harvesting has become a key factor in improving agricultural production efficiency and quality. Among these, the weighing of fruits and vegetables during harvest is an essential part of precision harvesting. With the widespread application of electronic scales, their role in fruit and vegetable harvesting on smart farms has become increasingly prominent. However, at present, fruit and vegetable harvesting still largely depends on manual operations, making the accurate recording of harvested fruits' weights and the scientific management of fruit yields particularly urgent.

Against this backdrop, this research conducts an in-depth survey of agricultural production activities, applying software engineering principles to identify and analyze specific requirements. It utilizes various software technologies, including web development techniques and YOLO-based fruit and vegetable recognition technologies, to design and develop a cloud-based agricultural fruit weighing software. This software achieves stable and high-performance data processing capabilities, provides efficient and rich information management functions, and offers multi-dimensional data visualization. Finally, the software's various functionalities were tested, and performance tests on key functionalities were conducted in specific hardware environments, demonstrating the core indicators of the software to meet the deployment needs in practical production environments.

In conclusion, the cloud-based agricultural fruit weighing software developed in this study provides an efficient, stable, and feature-rich solution for smart farm fruit harvesting and weighing management, contributing to the advancement of precision harvesting and digital management in smart farms.

>>>>

As modern agriculture advances toward intelligent transformation, the accurate collection of fruit weighing data has become a critical foundation for achieving efficient management and informed decision-making. Traditional weighing processes often face issues such as delayed data recording, frequent manual intervention, and poor device compatibility, which significantly hinder the efficiency and reliability of agricultural yield statistics.

To address these challenges, this paper proposes and implements a cloud-based agricultural fruit weighing software system that integrates multi-protocol communication, image recognition, and data management. The system adopts a cloud-edge collaborative architecture: on the farm-side edge, fruit images and weight data are collected in real time, and a YOLO-based image recognition algorithm is used to identify fruit types before publishing the weighing messages. On the cloud side, these messages from electronic scales are subscribed to, followed by data processing and storage. The software supports multiple communication protocols, including MQTT, HTTP, and CoAP, ensuring compatibility with various types of weighing hardware for flexible integration and rapid deployment. A data management and visualization platform is developed using Spring Boot and Vue, offering efficient information management and multi-dimensional data visualization capabilities.

This study includes comprehensive functional testing and performance evaluation under specific hardware conditions, demonstrating the core performance metrics of the system. The proposed solution provides an efficient, stable, and feature-rich platform for fruit weighing and data management in smart farming, supporting precision harvesting and the digital transformation of agriculture.

### 2025-05-09 paper/abs_zh.tex
feat: polish19

为解决上述瓶颈，本文提出并实现了一套融合多协议通信、图像识别与数据管理的农业果实称重云端软件。软件的整体架构采用云边端协同的模式进行设计，实现了两端数据处理的独立性。农场边端实时采集果实图像与重量信息，使用基于 YOLO 的图像识别技术识别出果实种类，最后发布称重消息。云端订阅电子秤上报的称重消息，完成后续的数据处理与存储。软件支持通过 MQTT、HTTP、CoAP 等多种通信协议发布称重消息，适配多类型称重硬件，可实现灵活接入与快速部署。软件使用 Spring Boot + Vue 技术构建农场数据管理与可视化平台，提供了高效且丰富的信息管理功能以及多个维度下数据的可视化。研究完成了对软件各项功能的测试以及在特定硬件环境下针对多个关键功能的性能测试，展现软件各项核心指标，以满足实际生产环境下软件的部署需求。

综上所述，本研究实现的农业果实称重云端软件为智慧农场的果实称重和数据管理提供了一个高效、稳定且功能丰富的解决方案，有助于推动智慧农场的精准收获和数字化管理。

>>>>

为解决上述瓶颈，本文提出并实现了一套融合多协议通信、图像识别与数据管理的农业果实称重云端软件。软件的整体架构采用云边协同的模式进行设计，农场边端实时采集果实图像与重量信息，使用基于 YOLO 的图像识别技术识别出果实种类，最后发布称重消息。云端订阅电子秤上报的称重消息，完成后续的数据处理与存储。软件支持通过 MQTT、HTTP、CoAP 等多种通信协议发布称重消息，适配多类型称重硬件，可实现灵活接入与快速部署。软件使用 Spring Boot + Vue 技术构建农场数据管理与可视化平台，提供了高效且丰富的信息管理功能以及多个维度下数据的可视化。

本研究完成了对软件各项功能的测试以及在特定硬件环境下针对多个关键功能的性能测试，展现了软件各项核心指标，满足实际生产环境下软件的部署需求，为智慧农场的果实称重和数据管理提供了一个高效、稳定且功能丰富的解决方案，有助于推动智慧农场的精准收获和数字化管理。
